\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test with Stationary Time Series

### 2023-11-07 manuscript/manuscript.tex
10/25 Notes
Figures

@@

>>>>

We constructed Q-Q plots of the distribution of the p-values to see if they are
normally distributed. A zoomed in plot for probabilities between 0 and 0.1, as
that is the most common range for significance levels $\alpha$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/sim_800_normal_-0.4_0}
  \caption{Q-Q p}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/zoom_800_normal_-0.4_0}
  \caption{}
  \label{fig:mu}
\end{figure}

@@

We expect the distribution of Microsoft stock returns to have a slightly
heavier tail than the normal distribution. We can test that it is normally
distributed (which we expect to reject). Then we can try testing if it follows
the $t$ distribution with different degrees of freedoms.
